Dominance Regions for Rank Two Cluster Algebras

### 2022-04-07 dominance_regions.tex
Monotonicity

  \begin{lemma}
    We have
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
  \end{lemma}
  \begin{proof}
    For any $i\ge 1$, we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
    It follows that
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
    which is equivalent to the desired expression.
    Similarly, 
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
    so that
    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
    which is again equivalent to the desired expression.
  \end{proof}

>>>>

  \begin{lemma}
    We have
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
    Moreover, each of these sequences is monotonic.
  \end{lemma}
  \begin{proof}
    For any $i\ge 1$, we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
    It follows that
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
    which is equivalent to the desired expression.
    Similarly, 
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
    so that
    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
    which is again equivalent to the desired expression.

    For the final claim, observe that $\frac{-u_{i,-\varepsilon}}{u_{i-1,\varepsilon}}<\frac{-u_{i+1,-\varepsilon}}{u_{i,\varepsilon}}$ and $\frac{-u_{i,-\varepsilon}}{u_{i+1,\varepsilon}}<\frac{-u_{i-1,-\varepsilon}}{u_{i,\varepsilon}}$ are both equivalent to $u_{i+1,-\varepsilon}u_{i-1,\varepsilon}<u_{i,-\varepsilon}u_{i,\varepsilon}$.
    This is immediate from the following induction:
    \begin{align*}
      u_{i+1,-\varepsilon}u_{i-1,\varepsilon}
      &=(cu_{i,\varepsilon}-u_{i-1,-\varepsilon})u_{i-1,\varepsilon}
      =cu_{i,\varepsilon}u_{i-1,\varepsilon}-u_{i-1,-\varepsilon}u_{i-1,\varepsilon}\\
      &<cu_{i,\varepsilon}u_{i-1,\varepsilon}-u_{i,\varepsilon}u_{i-2,-\varepsilon}
      =u_{i,\varepsilon}(cu_{i-1,\varepsilon}-u_{i-2,-\varepsilon})\\
      &=u_{i,\varepsilon}u_{i,-\varepsilon}.
    \end{align*}
  \end{proof}
